### 2022-01-27 documentos/pce.tex
Títulos y referencias a secciones

\section{PCE Maps} 
To introduce the family of Pauli component erasing maps we start  
reviewing basic concepts of quantum channels that will allow us to introduce some 
notation. 
% In this section we introduce the definition of Pauli component erasing maps,
% but first we go through several standard definitions needed to discuss them.
\subsection{Quantum channels} % {{{
Quantum channels are the most general linear operations that a quantum
system undergo independently of its past~\cite{zimansbook,cirac}.
The physical system under study will be associated with a Hilbert space
denoted by \hilbert{}, and the set of linear operators over such space will 
be denoted by $\mcB(\hilbert)$. That way, a density matrix $\rho$ of such system
 is an element of $\mcB(\hilbert)$.

>>>>

\section{PCE Maps}
\janote{Propuesta: hacer un switch de títulos entre el título de II y de II.B}
\janote{En este primer agregué las referencias a en cuáles secciones hablamos de qué}
To introduce in \ref{sec:single:qubit} the family of Pauli component erasing 
maps we start in \ref{subsec:qtm_ch} reviewing basic concepts of quantum 
channels that will allow us to introduce some notation. 
% In this section we introduce the definition of Pauli component erasing maps,
% but first we go through several standard definitions needed to discuss them.
\subsection{Quantum channels} \label{subsec:qtm_ch}% {{{
Quantum channels are the most general linear operations that a quantum
system undergo independently of its past~\cite{zimansbook,cirac}.
The physical system under study will be associated with a Hilbert space
denoted by \hilbert{}, and the set of linear operators over such space will 
be denoted by $\mcB(\hilbert)$. That way, a density matrix $\rho$ of such system
 is an element of $\mcB(\hilbert)$.
